---
title: "bendable_analyses"
date: "2025-04-16"
output: 
  html_document:
    theme: flatly          
    highlight: tango       
    toc: true               
    toc_depth: 2            
    toc_float: true         
    number_sections: true   
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("tidyverse")
#install.packages("skimr")
#install.packages("psych")
#install.packages("kableExtra")
#install.packages("scales")
#install.packages("wordcloud")
#install.packages("tidytext")
#install.packages("RColorBrewer")
#install.packages("topicmodels")
#install.packages("reshape2")
library(tidyverse)
library(skimr)
library(psych)
library(kableExtra)
library(scales)
library(wordcloud)
library(tidytext)
library(RColorBrewer)
library(topicmodels)
library(reshape2)

#read in data

pps <- read_csv("data/PPS Data for Osmind-Clean - PPS Data.csv")
pss1 <- read_csv("data/PSS1 Data for Osmind-Clean - PSS1 Data.csv")
pss2 <- read_csv("data/PSS2 Data for Osmind-Clean - PSS2 Data.csv")
participant_info <- read_csv("data/Research Participant Info for Osmind-Clean - Sheet5.csv")
screen_a1 <- read_csv("data/Screening Application (A01) data for Osmind-Clean - A01 Data.csv") 
screen_b1 <- read_csv("data/Screening Interview (B01) for Osmind-Clean - B01 Data.csv")


#process

screen_a1_working <- screen_a1 %>% 
  mutate(a01_pronouns = as.factor(a01_pronouns),
         a01_state = as.factor(a01_state),
         a01_legalsex = as.factor(a01_legalsex),
         a01_birthsex = as.factor(a01_birthsex),
         a01_race = as.factor(a01_race),
         a01_ethnic = as.factor(a01_ethnic),
         a01_education = as.factor(a01_educ))

master <- pss2 %>% 
  left_join(screen_a1_working, by = c("id")) %>% 
  left_join(pss1, by = c("id")) %>% 
  left_join(pps, by = c("id"))

who_a01_response_map <- c(
  "At no time" = 0,
  "Some of the time" = 1,
  "Less than half of the time" = 2,
  "More than half of the time" = 3,
  "Most of the time" = 4,
  "All the time" = 5
) 

who_response_map <- c(
  "At no time" = 0,
  "Some of the time" = 1,
  "Less than half the time" = 2,
  "More than half the time" = 3,
  "Most of the time" = 4,
  "All the time" = 5
)

phq_response_map <- c(
  "Not at all" = 0,
  "Several days" = 1,
  "More than half of the days" = 2,
  "Nearly every day" = 3
)

gad_response_map <- c(
  "Not at all" = 0,
  "Several days" = 1,
  "More than half of the days" = 2,
  "Nearly every day" = 3
)

a01_who_items <- paste0("a01_who", 1:5)
pss1_who_items <- paste0("pss1_who", 1:5)
pss2_who_items <- paste0("pss2_who", 1:5)
a01_phq_items <- paste0("a01_phq", 1:8)
pss1_phq_items <- paste0("pss1_phq", 1:8)
pss2_phq_items <- paste0("pss2_phq", 1:8)
a01_gad_items <- paste0("a01_gad", 1:7)
pss1_gad_items <- paste0("pss1_gad", 1:7)
pss2_gad_items <- paste0("pss2_gad", 1:7)

master <- master %>%
  mutate(across(all_of(a01_who_items), ~ recode(. , !!!who_response_map), .names = "{.col}_num"),
         across(all_of(a01_phq_items), ~ recode(. , !!!phq_response_map), .names = "{.col}_num"),
         across(all_of(a01_gad_items), ~ recode(. , !!!gad_response_map), .names = "{.col}_num"),
         across(all_of(pss1_who_items), ~ recode(. , !!!who_response_map), .names = "{.col}_num"),
         across(all_of(pss2_who_items), ~recode(. , !!!who_response_map), .names = "{.col}_num"),
         across(all_of(pss1_phq_items), ~recode(. , !!!phq_response_map), .names = "{.col}_num"),
         across(all_of(pss2_phq_items), ~recode(. , !!!phq_response_map), .names = "{.col}_num"),
         across(all_of(pss1_gad_items), ~recode(. , !!!gad_response_map), .names = "{.col}_num"),
         across(all_of(pss2_gad_items), ~recode(. , !!!gad_response_map), .names = "{.col}_num")) 

#get totall scores for survyes

master <- master %>% 
  mutate(
         pss1_phq_total = rowSums(select(., pss1_phq1_num:pss1_phq8_num), na.rm = TRUE),
         pss2_phq_total = rowSums(select(., pss2_phq1_num:pss2_phq8_num), na.rm = TRUE),
         pss1_gad_total = rowSums(select(., pss1_gad1_num:pss1_gad7_num), na.rm = TRUE),
         pss2_gad_total = rowSums(select(., pss2_gad1_num:pss2_gad7_num), na.rm = TRUE),
         pss1_who_total = rowSums(select(., pss1_who1_num:pss1_who5_num), na.rm = TRUE),
         pss2_who_total = rowSums(select(., pss2_who1_num:pss2_who5_num), na.rm = TRUE),
         )
```

Below is a summary of participant demographics, psilocybin experience, mental health experience, medical background, and baseline scores on three questionnaires: the WHO-5, PHQ-9, and GAD-7. The summary is organized into two tabs corresponding to two distinct samples (1) participants who completed the screening process (n = 308), and those who participated in treatment and completed follow-up assessments (n = 88)

## Demographics {.tabset}

### Screened participants (n = 308)

```{r}

#all screened participants (n = 308)

summary(screen_a1_working$a01_age)

#legal sex
screen_a1_working %>%
  count(a01_legalsex) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(`Legal Sex` = a01_legalsex, N = n) %>%
  kable(format = "html", caption = "Legal Sex Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE)

#Birth sex
screen_a1_working %>%
  count(a01_birthsex) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(`Birth Sex` = a01_birthsex, N = n) %>%
  kable(format = "html", caption = "Birth Sex Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE)

#pronouns
screen_a1_working %>%
  count(a01_pronouns) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(`Pronouns` = a01_pronouns, N = n) %>%
  kable(format = "html", caption = "Pronouns Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE)



# Gender Identity
screen_a1_working %>%
  count(a01_gender) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(`Gender Identity` = a01_gender, N = n) %>%
  kable(format = "html", caption = "Gender Identity Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

# Race
screen_a1_working %>%
  count(a01_race) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Race = a01_race, N = n) %>%
  kable(format = "html", caption = "Race Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

# Ethnicity
screen_a1_working %>%
  count(a01_ethnic) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Ethnicity = a01_ethnic, N = n) %>%
  kable(format = "html", caption = "Ethnicity Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

#Hispanic
screen_a1_working %>%
  count(a01_hisplat) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Hisp_Lat = a01_hisplat, N = n) %>%
  kable(format = "html", caption = "Hispanic/Latino Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)


# Education
screen_a1_working %>%
  count(a01_educ) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Education = a01_educ, N = n) %>%
  kable(format = "html", caption = "Education Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

# Employment
screen_a1_working %>%
  count(a01_work) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(`Employment Status` = a01_work, N = n) %>%
  kable(format = "html", caption = "Employment Status Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

# Income
screen_a1_working %>%
  count(a01_income) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Income = a01_income, N = n) %>%
  kable(format = "html", caption = "Income Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

#state
screen_a1_working %>%
  count(a01_state) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(State = a01_state, N = n) %>%
  kable(format = "html", caption = "State Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

```

### Final Participants (n = 88)

```{r}


summary(master$a01_age)

#legal sex
master %>%
  count(a01_legalsex) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(`Legal Sex` = a01_legalsex, N = n) %>%
  kable(format = "html", caption = "Legal Sex Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE)

# Gender Identity
master %>%
  count(a01_gender) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(`Gender Identity` = a01_gender, N = n) %>%
  kable(format = "html", caption = "Gender Identity Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

# Race
master %>%
  count(a01_race) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Race = a01_race, N = n) %>%
  kable(format = "html", caption = "Race Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

# Ethnicity
master %>%
  count(a01_ethnic) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Ethnicity = a01_ethnic, N = n) %>%
  kable(format = "html", caption = "Ethnicity Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

# hispaniclatino
master %>%
  count(a01_hisplat) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Hispanic_Latino = a01_hisplat, N = n) %>%
  kable(format = "html", caption = "Hispanic/Latino Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

# Education
master %>%
  count(a01_educ) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Education = a01_educ, N = n) %>%
  kable(format = "html", caption = "Education Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

# Employment
master %>%
  count(a01_work) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(`Employment Status` = a01_work, N = n) %>%
  kable(format = "html", caption = "Employment Status Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

# Income
master %>%
  count(a01_income) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Income = a01_income, N = n) %>%
  kable(format = "html", caption = "Income Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE)

```

## Psilocybin Experience {.tabset}

### Screened sample 

```{r}
screen_a1_working %>%
  count(a01_psychexp) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Experience = a01_psychexp, N = n) %>%
  kable(format = "html", caption = "Experience with Psilocybin or Psychedelics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_nonord) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Non_ordinary_states = a01_nonord, N = n) %>%
  kable(format = "html", caption = "Experience with Non-ordinary States of Consciousness") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_nonord) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Non_ordinary_states = a01_nonord, N = n) %>%
  kable(format = "html", caption = "Experience with Non-ordinary States of Consciousness") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_prepare) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Preparedness = a01_prepare, N = n) %>%
  kable(format = "html", caption = "Preparedness") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_barrier) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Barriers = a01_barrier, N = n) %>%
  kable(format = "html", caption = "Barriers to Psilocybin Services Access") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

```

### Final sample

```{r}
master %>%
  count(a01_psychexp) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Experience = a01_psychexp, N = n) %>%
  kable(format = "html", caption = "Experience with Psilocybin or Psychedelics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

master %>%
  count(a01_nonord) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Non_ordinary_states = a01_nonord, N = n) %>%
  kable(format = "html", caption = "Experience with Non-ordinary States of Consciousness") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

master %>%
  count(a01_nonord) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Non_ordinary_states = a01_nonord, N = n) %>%
  kable(format = "html", caption = "Experience with Non-ordinary States of Consciousness") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

master %>%
  count(a01_prepare) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Preparedness = a01_prepare, N = n) %>%
  kable(format = "html", caption = "Preparedness") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

master %>%
  count(a01_barrier) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Barriers = a01_barrier, N = n) %>%
  kable(format = "html", caption = "Barriers to Psilocybin Services Access") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 
```

## Mental health Experience {.tabset}

### Screened participants

```{r}
screen_a1_working %>%
  count(a01_pastther) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Past_Therapy = a01_pastther, N = n) %>%
  kable(format = "html", caption = "Mental health therapy (past)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_nowther) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Now_Therapy = a01_nowther, N = n) %>%
  kable(format = "html", caption = "Mental health therapy (current)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_pastout) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Past_Outpatient = a01_pastout, N = n) %>%
  kable(format = "html", caption = "Mental health Outpatient (past)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_nowout) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Now_Outpatient = a01_nowout, N = n) %>%
  kable(format = "html", caption = "Mental health Outpatient (current)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_famhx) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Family_History = a01_famhx, N = n) %>%
  kable(format = "html", caption = "Family History of Psychotic Disorders") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_hosp) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Hospitalized = a01_hosp, N = n) %>%
  kable(format = "html", caption = "Hospitalized for Mental Health") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_nowharm) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Current_harm = a01_nowharm, N = n) %>%
  kable(format = "html", caption = "Thoughts of causing harm (current)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_pastharm) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Past_harm = a01_pastharm, N = n) %>%
  kable(format = "html", caption = "Thoughts of causing harm (past)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_support) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Support = a01_support, N = n) %>%
  kable(format = "html", caption = "Mental health support system") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

```

### Final participants

```{r}

```

## Medical History {.tabset}

### Screened Particiapnts

```{r}

screen_a1_working %>%
  count(a01_nowrx) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Medication = a01_nowrx, N = n) %>%
  kable(format = "html", caption = "Current medications") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_pastrx) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Medication = a01_pastrx, N = n) %>%
  kable(format = "html", caption = "Past medications") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 


screen_a1_working %>%
  count(a01_lithium) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Lithium = a01_lithium, N = n) %>%
  kable(format = "html", caption = "Lithium in the past 30 days") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 


screen_a1_working %>%
  count(a01_pregnant) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Pregnant= a01_pregnant, N = n) %>%
  kable(format = "html", caption = "Currently Pregnant") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_breastfeed) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Breastfeed = a01_breastfeed, N = n) %>%
  kable(format = "html", caption = "Currently Breastfeeding") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_hxbp) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Blood_pressure = a01_hxbp, N = n) %>%
  kable(format = "html", caption = "History of Uncontrolled Blood Pressure or Heart Disease") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_vet) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Veteran = a01_vet, N = n) %>%
  kable(format = "html", caption = "Served in the Armed Forces") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_group) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Group = a01_group, N = n) %>%
  kable(format = "html", caption = "Interest in Group Research") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 

screen_a1_working %>%
  count(a01_finaid) %>%
  mutate(Percent = percent(n / sum(n))) %>%
  rename(Financial_aid = a01_finaid, N = n) %>%
  kable(format = "html", caption = "Interest in Financial Aid") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) 
```

### Final Participants

```{r}

```

## WHO {.tabset}

### Screened participants

```{r}

#who 1
who1_data <- screen_a1_working %>%
  count(a01_who1, name = "Count") %>%
  mutate(Percent = Count / sum(Count),
         Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")"))


ggplot(who1_data, aes(x = reorder(a01_who1, -Count), y = Count)) +
  geom_col(fill = "#4682B4") +
  geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +  # adds 10% space on top
  labs(
    x = "Responses",
    y = "Number of Participants",
    title = "WHO 1",
    subtitle = "Over the last 2 weeks, I have felt cheerful and in good spirits"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#who2
who2_data <- screen_a1_working %>%
  count(a01_who2, name = "Count") %>%
  mutate(Percent = Count / sum(Count),
         Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")"))

ggplot(who2_data, aes(x = reorder(a01_who2, -Count), y = Count)) +
  geom_col(fill = "#4682B4") +
  geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) + 
  labs(
    x = "Responses",
    y = "Number of Participants",
    title = "WHO 2",
    subtitle = "Over the last 2 weeks, I have felt calm and relaxed"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#who3
who3_data <- screen_a1_working %>%
  count(a01_who3, name = "Count") %>%
  mutate(Percent = Count / sum(Count),
         Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")"))

ggplot(who3_data, aes(x = reorder(a01_who3, -Count), y = Count)) +
  geom_col(fill = "#4682B4") +
  geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) + 
  labs(
    x = "Responses",
    y = "Number of Participants",
    title = "WHO 3",
    subtitle = "Over the last 2 weeks, I have felt alive and vigorous"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#who4
who4_data <- screen_a1_working %>%
  count(a01_who4, name = "Count") %>%
  mutate(Percent = Count / sum(Count),
         Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")"))

ggplot(who4_data, aes(x = reorder(a01_who4, -Count), y = Count)) +
  geom_col(fill = "#4682B4") +
  geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) + 
  labs(
    x = "Responses",
    y = "Number of Participants",
    title = "WHO 4",
    subtitle = "Over the last 2 weeks, I woke up feeling fresh and rested"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#who5
who5_data <- screen_a1_working %>%
  count(a01_who5, name = "Count") %>%
  mutate(Percent = Count / sum(Count),
         Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")"))

ggplot(who5_data, aes(x = reorder(a01_who5, -Count), y = Count)) +
  geom_col(fill = "#4682B4") +
  geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) + 
  labs(
    x = "Responses",
    y = "Number of Participants",
    title = "WHO 5",
    subtitle = "Over the last 2 weeks, my daily life has been filled with things that interest me"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

### Final participants

```{r}
#who 1
who1_data <- master %>%
  count(a01_who1, name = "Count") %>%
  mutate(Percent = Count / sum(Count),
         Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")"))


ggplot(who1_data, aes(x = reorder(a01_who1, -Count), y = Count)) +
  geom_col(fill = "#4682B4") +
  geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +  # adds 10% space on top
  labs(
    x = "Responses",
    y = "Number of Participants",
    title = "WHO 1",
    subtitle = "Over the last 2 weeks, I have felt cheerful and in good spirits"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#who2
who2_data <- master %>%
  count(a01_who2, name = "Count") %>%
  mutate(Percent = Count / sum(Count),
         Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")"))

ggplot(who2_data, aes(x = reorder(a01_who2, -Count), y = Count)) +
  geom_col(fill = "#4682B4") +
  geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) + 
  labs(
    x = "Responses",
    y = "Number of Participants",
    title = "WHO 2",
    subtitle = "Over the last 2 weeks, I have felt calm and relaxed"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#who3
who3_data <- master %>%
  count(a01_who3, name = "Count") %>%
  mutate(Percent = Count / sum(Count),
         Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")"))

ggplot(who3_data, aes(x = reorder(a01_who3, -Count), y = Count)) +
  geom_col(fill = "#4682B4") +
  geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) + 
  labs(
    x = "Responses",
    y = "Number of Participants",
    title = "WHO 3",
    subtitle = "Over the last 2 weeks, I have felt alive and vigorous"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#who4
who4_data <- master %>%
  count(a01_who4, name = "Count") %>%
  mutate(Percent = Count / sum(Count),
         Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")"))

ggplot(who4_data, aes(x = reorder(a01_who4, -Count), y = Count)) +
  geom_col(fill = "#4682B4") +
  geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) + 
  labs(
    x = "Responses",
    y = "Number of Participants",
    title = "WHO 4",
    subtitle = "Over the last 2 weeks, I woke up feeling fresh and rested"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#who5
who5_data <- master %>%
  count(a01_who5, name = "Count") %>%
  mutate(Percent = Count / sum(Count),
         Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")"))

ggplot(who5_data, aes(x = reorder(a01_who5, -Count), y = Count)) +
  geom_col(fill = "#4682B4") +
  geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) + 
  labs(
    x = "Responses",
    y = "Number of Participants",
    title = "WHO 5",
    subtitle = "Over the last 2 weeks, my daily life has been filled with things that interest me"
  ) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## PHQ {.tabset}

### Screened participants - frequency


```{r}

phq_labels <- c(
  a01_phq1 = "Little interest or pleasure in doing things",
  a01_phq2 = "Feeling down, depressed, or hopeless",
  a01_phq3 = "Trouble falling/staying asleep or sleeping too much",
  a01_phq4 = "Feeling tired or having little energy",
  a01_phq5 = "Poor appetite or overeating",
  a01_phq6 = "Feeling bad about yourself",
  a01_phq7 = "Trouble concentrating",
  a01_phq8 = "Moving/speaking slowly or being fidgety/restless",
  a01_phq9 = "Thoughts that you'd be better off dead or hurting yourself"
)


phq_plots_screen <- imap(phq_labels, function(label, var) {
  screen_a1_working %>%
    count(.data[[var]], name = "Count") %>%
    mutate(
      Percent = Count / sum(Count),
      Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")")
    ) %>%
    ggplot(aes(x = reorder(.data[[var]], -Count), y = Count)) +
    geom_col(fill = "#4682B4") +
    geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
    labs(
      x = "Responses",
      y = "Number of Participants",
      title = paste0("PHQ ", gsub(".*phq", "", var)),
      subtitle = label
    ) +
    theme_minimal(base_size = 14) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
})


#loop
walk(phq_plots_screen, print)  

##



phq_items <- paste0("a01_phq", 1:9)

screen_a1_working <- screen_a1_working %>%
  mutate(across(all_of(phq_items), ~ recode(. , !!!phq_response_map), .names = "{.col}_num")) %>%
  mutate(phq_screen_total = rowSums(across(ends_with("_num")), na.rm = TRUE))


summary(screen_a1_working$phq_screen_total)


```



### Final participants

```{r}


phq_plots_master <- imap(phq_labels, function(label, var) {
  master %>%
    count(.data[[var]], name = "Count") %>%
    mutate(
      Percent = Count / sum(Count),
      Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")")
    ) %>%
    ggplot(aes(x = reorder(.data[[var]], -Count), y = Count)) +
    geom_col(fill = "#4682B4") +
    geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
    labs(
      x = "Responses",
      y = "Number of Participants",
      title = paste0("PHQ ", gsub(".*phq", "", var)),
      subtitle = label
    ) +
    theme_minimal(base_size = 14) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
})


#loop
walk(phq_plots_master, print)  
```

### PHQ Change

```{r}

```


## GAD {.tabset}

### Screened participants

```{r}
# GAD labels
gad_labels <- c(
  a01_gad1 = "Feeling nervous, anxious, or on edge",
  a01_gad2 = "Not being able to stop or control worrying",
  a01_gad3 = "Worrying too much about different things",
  a01_gad4 = "Trouble relaxing",
  a01_gad5 = "Being so restless that it is hard to sit still",
  a01_gad6 = "Becoming easily annoyed or irritable",
  a01_gad7 = "Feeling afraid as if something awful might happen",
  a01_gad8 = "How difficult have these problems made it for you to function"
)


gad_plots_screen <- imap(gad_labels, function(label, var) {
  screen_a1_working %>%
    count(.data[[var]], name = "Count") %>%
    mutate(
      Percent = Count / sum(Count),
      Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")")
    ) %>%
    ggplot(aes(x = reorder(.data[[var]], -Count), y = Count)) +
    geom_col(fill = "#4682B4") +
    geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
    labs(
      x = "Responses",
      y = "Number of Participants",
      title = paste0("GAD ", gsub(".*gad", "", var)),
      subtitle = label
    ) +
    theme_minimal(base_size = 14) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
})


walk(gad_plots_screen, print)

```

### Final participants

```{r}
gad_plots_master <- imap(gad_labels, function(label, var) {
  master %>%
    count(.data[[var]], name = "Count") %>%
    mutate(
      Percent = Count / sum(Count),
      Label = paste0(Count, " (", percent(Percent, accuracy = 1), ")")
    ) %>%
    ggplot(aes(x = reorder(.data[[var]], -Count), y = Count)) +
    geom_col(fill = "#4682B4") +
    geom_text(aes(label = Label), vjust = -0.5, size = 3.5) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
    labs(
      x = "Responses",
      y = "Number of Participants",
      title = paste0("GAD ", gsub(".*gad", "", var)),
      subtitle = label
    ) +
    theme_minimal(base_size = 14) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
})


walk(gad_plots_master, print)
```

### GAD-7 Change

```{r}

```

## Qual Analyses {.tabset}

### 

```{r}
a01_reason_text_data <- screen_a1 %>%
  select(a01_reason) %>%
  unnest_tokens(word, a01_reason) %>%
  anti_join(stop_words) %>%  # remove common words like "the", "and", etc.
  count(word, sort = TRUE)

# View top words
head(a01_reason_text_data, 20)

#word cloud
wordcloud(words = a01_reason_text_data$word, freq = a01_reason_text_data$n, min.freq = 15)

wordcloud(
  words = a01_reason_text_data$word,
  freq = a01_reason_text_data$n,
  min.freq = 15,
  max.words = 100,
  random.order = FALSE,
  rot.per = 0.15,
  colors = brewer.pal(8, "Dark2"),
  scale = c(4, 0.5)  
)

title("Reasons for Seeking Treatment", cex.main = 1.0)

#


# Preprocess and cast to document-term matrix
dtm <- screen_a1 %>%
  mutate(doc_id = row_number()) %>%
  unnest_tokens(word, a01_reason) %>%
  anti_join(stop_words) %>%
  count(doc_id, word) %>%
  cast_dtm(doc_id, word, n)

# Run LDA topic model (e.g., 3 topics)
lda_model <- LDA(dtm, k = 3, control = list(seed = 1234))
topics <- tidy(lda_model, matrix = "beta")

# Top words per topic
top_terms <- topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 5) %>%
  ungroup()

top_terms

```

